Simulation Explorer

### 2018-06-28 inst/rmd/vis_sim.Rmd
Add survey distribution, estimates and error plots to flexdashboard

---
title: "Simulation Explorer"
output: flexdashboard::flex_dashboard
always_allow_html: yes
---

```{r setup, echo=FALSE}
library(plotly)
library(viridis)
knitr::opts_chunk$set(echo = FALSE, fig.height = 7, fig.width = 8)
```

@@

```{r, eval = "sp_N" %in% names(sim)}
renderPlotly({
  plot_distribution(sim, ages = input$age, year = input$year, type = input$type,
                    scale = input$scale)
})

@@

>>>>

---
title: "Simulation Explorer"
output: flexdashboard::flex_dashboard
runtime: shiny
---

```{r setup, echo=FALSE}
library(plotly)
library(viridis)
knitr::opts_chunk$set(echo = FALSE, fig.height = 7, fig.width = 8, cache = FALSE)
```

@@

```{r, eval = "sp_N" %in% names(sim)}
renderPlotly({
  plot_distribution(sim, ages = input$age, year = input$year, type = input$type,
                    scale = input$scale, axes = FALSE)
})

@@

Survey { `r if(!"sp_I" %in% names(sim)) ".hidden"`}
================================================================================

```{r}
sliderInput("samp_year", "Year", 
            min = min(sim$years), max = max(sim$years), 
            value = 1, step = 1)
sliderInput("samp_sim", "Simulation", 
            min = min(sim$setdet$sim), max = max(sim$setdet$sim), 
            value = 1, step = 1)
```

### Survey sampling

```{r, eval = "sp_I" %in% names(sim)}
renderPlotly({
  plot_samp_dist(sim, which_year = input$samp_year, which_sim = input$samp_sim)
})
```

Estimates { `r if(!"age_strat_error" %in% names(sim)) ".hidden"`}
================================================================================

```{r}
selectInput("set_den", "Set density", 
            choices = sort(unique(sim$surveys$set_den)))
selectInput("lengths_cap", "max(lengths)", 
            choices = sort(unique(sim$surveys$lengths_cap)))
selectInput("ages_cap", "max(ages)", 
            choices = sort(unique(sim$surveys$ages_cap)))
selectInput("facet_by", "Facet by", 
            choices = c("age", "year"))
```

### True population size vs. stratified estimates

```{r, eval = "age_strat_error" %in% names(sim)}
renderPlotly({
  surveys <- sim$surveys
  i <- surveys$survey[surveys$set_den == input$set_den & 
                      surveys$lengths_cap == input$lengths_cap &
                      surveys$ages_cap == input$ages_cap]
  plot_true_vs_est(sim, which_survey = i, facet_by = input$facet_by,
                   max_sims = 100)
})
```

Error { `r if(!"surveys" %in% names(sim)) ".hidden"`}
================================================================================

Column  {.tabset}
--------------------------------------------------------------------------------

### Error surface

```{r, eval = "surveys" %in% names(sim)}
plot_error_surface(sim)
```

### Error cross-sections

```{r, eval = "surveys" %in% names(sim)}
plot_error_cross_sections(sim)
```
